An Empirical Analysis of the Role of Energy in Economic Growth

### 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Deleting .pdf and .tex files for EconGrowth4.

\usepackage{wrapfig}    % Allows wrapping of text around figures
\usepackage{soul}       % Provides strikethrough text
\usepackage{float}      % Allows precise positioning of tables and figures within the text
\usepackage{amsmath}    % Allows \begin{equation*} \end{equation*} for unnumbered equations
\usepackage{multirow}   % To create multirow tables
\usepackage{hyperref}   % To create hyperlinks in the paper
\usepackage{microtype}  % produces hanging punctuation and beautiful type
\usepackage{booktabs}   % produces beautiful tables
\usepackage{tablefootnote}  % allows footnotes in tables

@@

It is important to note that large residuals can arise from either
(a) poor quality historical time series data, or 
(b) a mathematical model that does not describe the underlying phenomena well.
It is also important to note that (c) even when the residuals are small and the 
model produces fitted values that track the observed data closely, it may
yet be difficult to estimate some or all of the model parameters precisely.
The resampling method employed herein reflects all three of these potential 
sources of uncertainty in parameter estimates.

We choose the resampling approach instead of the more-common technique 
of estimating confidence intervals from standard errors for two reasons. 
First, model parameters are highly constrained, and confidence intervals often violate the constraints. 
For example a result of $\alpha = 0.25 \pm 0.3$ is nonsensical, 
because $ \alpha \in [0, 1]$. 
Second, true confidence intervals for constrained parameters are often asymmetric
(e.g., $\alpha = 0.2 + 0.1, -0.05$), 
but the standard error approach yields symmetric confidence intervals. 
The resampling approach that we employed both respects constraints 
and allows for asymmetric confidence intervals.%
  \footnote{
  In addition, we choose to present parameter uncertainty results visually 
  (see Figures~\ref{fig:CD_lambda_theta_graph}, \ref{fig:CD_Ternary_Scatter_Graph},
  \ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}, and
  \ref{fig:LINEXq_Resample_Graph}),
  both because the resampling technique lends itself to visual presentation and 
  because we believe visual comparison is more effective than tables of numbers.
  }

@@

Figure~\ref{fig:CD_lambda_theta_graph} shows $\lambda$ and $\theta$ values
for Cobb-Douglas resample models with and without energy.
Each reample is shown as a gray dot on the graph. 
The fit to historical data is shown as a gray crosshairs.

Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (without and with energy) resample models.

>>>>

\usepackage{wrapfig}    % Allows wrapping of text around figures
\usepackage{soul}       % Provides strikethrough text
\usepackage{float}      % Allows precise positioning of tables and figures within the text
\usepackage{amsmath}    % Allows \begin{equation*} \end{equation*} for unnumbered equations
\usepackage{multirow}   % To create multirow tables
\usepackage{hyperref}   % To create hyperlinks in the paper
\usepackage{microtype}  % produces hanging punctuation and beautiful type
\usepackage{booktabs}   % produces beautiful tables
\usepackage{tablefootnote}  % allows footnotes in tables
\usepackage{nicefrac}   % Gives nice fractions

@@

It is important to note that large residuals can arise from either
poor quality historical time series data or 
a mathematical model that does not describe the underlying phenomena well.
It is also important to note that even when the residuals are small and the 
model produces fitted values that track the observed data closely, it may
yet be difficult to estimate some or all of the model parameters precisely.
The resampling method employed herein reflects all three of these potential 
sources of uncertainty in parameter estimates.

We choose the resampling approach instead of the more-common technique 
of estimating confidence intervals from standard errors for two reasons. 
First, model parameters are highly constrained, and confidence intervals often violate the constraints. 
For example a result of $\alpha = 0.25 \pm 0.3$ is nonsensical, 
because $ \alpha \in [0, 1]$. 
Second, true confidence intervals for constrained parameters are often asymmetric
(e.g., $\alpha = 0.2 + 0.1, -0.05$), 
but the standard error approach yields symmetric confidence intervals. 
The resampling approach that we employed both respects constraints 
and allows for asymmetric confidence intervals.%
  \footnote{
  In addition, we choose to present parameter uncertainty results visually 
  (see Figures~\ref{fig:CD_lambda_theta_graph}, \ref{fig:CD_Ternary_Scatter_Graph},
  \ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}, and
  \ref{fig:LINEXq_Resample_Graph}),
  both because the resampling technique lends itself to visual presentation and 
  because we believe visual comparison is more effective 
  in communicating results than endless tables of numbers.
  }

@@

Figure~\ref{fig:CD_lambda_theta_graph} shows $\lambda$ and $\theta$ values
for Cobb-Douglas resample models with and without energy.
Each resample is shown as a gray dot on the graph. 
The fit to historical data is shown as a gray crosshairs.

Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots%
  \footnote{
  Ternary plots are effective for communicating relationships among three variables
  that sum to a constant value.
  Each vertex is labeled with a variable ($\alpha$, $\beta$, or $\gamma$)
  whose value is unity at that location.
  For example, a data point at the top of the ternary plots in Figure~\ref{fig:CD_Ternary_Scatter_Graph}
  has $\gamma = 1$ and both $\alpha = 0$ and $\beta = 0$, 
  by the constant returns to scale assumption.
  Along each edge, the variable labeled at the opposite vertex is equal to zero.
  For example, a data point along the bottom edge 
  of the ternary plots in Figure~\ref{fig:CD_Ternary_Scatter_Graph}
  has $\gamma = 0$.
  A data point along the bottom edge and two-thirds of the way toward the $\beta$ vertex
  has $\alpha = \nicefrac{1}{3}$, $\beta = \nicefrac{2}{3}$, and $\gamma = 0$.
  }
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (without and with energy) resample models.
